Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal

### 2010-01-29 trunk/doc/msc-proposal/msc-snmp.tex
proposal: snmp operations

There are several types of defined applications (Figure \ref{fig:snmparch}), such as a command generator which monitor and manipulate management data, a command responder providing access to management data, a notification originator initiating asynchronous messages, a notification receiver processing these messages, and a proxy forwarder which forwards messages between entities. Applications may use the services provided by the SNMP engine. An SNMP entity which includes one or more command generator and notification receiver applications is called an SNMP manager. An entity containing one or more command generator and notification receiver applications is called an SNMP manager.
\section{Message Format}
The SNMPv3 message (Figure \ref{fig:snmp-format}) contains the SNMP version, fields for global data (such as the message identifier, the maximum message size, the security model and the level of security), fields for the security model information and naming scope (context identifier and name), and finally the protocol data unit (PDU).
\begin{figure}[htp]	
\begin{center}
    \includegraphics[scale = 0.60]{img/snmpv3-message.pdf}
    \caption{SNMPv3 message format}   
	\label{fig:snmp-format}
\end{center}
\end{figure}

@@

The naming scope contains a PDU and the context in which it has to be processed. The context engineID identifies the engine  and the context name defines the particular context associated with the management information contained in the PDU of the message. These fields are followed by the PDU data.

\section{Protocol Operations}

>>>>

There are several types of defined applications (Figure \ref{fig:snmparch}), such as a command generator which monitor and manipulate management data, a command responder providing access to management data, a notification originator initiating asynchronous messages, a notification receiver processing these messages, and a proxy forwarder which forwards messages between entities. Applications may use the services provided by the SNMP engine. An SNMP entity which includes one or more command generator and notification receiver applications is called an SNMP manager. An entity containing one or more command generator and notification receiver applications is called an SNMP manager.

\section{Message Format}\label{sec:messformat}
The SNMPv3 message (Figure \ref{fig:snmp-format}) contains the SNMP version, fields for global data (such as the message identifier, the maximum message size, the security model and the level of security), fields for the security model information and naming scope (context identifier and name), and finally the protocol data unit (PDU).
\begin{figure}[htp]	
\begin{center}
    \includegraphics[scale = 0.60]{img/snmpv3-message.pdf}
    \caption{SNMPv3 message format}   
	\label{fig:snmp-format}
\end{center}
\end{figure}

@@

The naming scope contains a PDU and the context in which it has to be processed. The context engineID identifies the engine which realizes the managed objects referenced within the PDU, and the context name defines the particular context associated with the management information contained in the PDU of the message. These fields are followed by the PDU data.

\section{Protocol Operations}
As described in Section \ref{sec:messformat}, an SNMP message encapsulates a PDU which specifies the operations performed by the receiving SNMP engine. The SNMP protocol defines PDUs for the following operations: Get, GetNext, GetBulk, Response, Set, Trap, Inform.

In addition, the Report protocol operation can be used internally to allow SNMP engines to communicate with each other for error notifications and clock synchronization.
